\documentclass[helvetica,openbib,nologo,notitle]{europecv}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage[a4paper,top=1.27cm,left=1cm,right=1cm,bottom=2cm]{geometry}
\usepackage[english]{babel}
\usepackage{bibentry}
\usepackage{url}

\renewcommand{\ttdefault}{phv} % Uses Helvetica instead of fixed width font

\ecvname{Iovene, Salvatore}
\ecvfootername{Salvatore Iovene}
\ecvaddress{Riimukallio 5 A 4, 02760 Espoo, Finland}
\ecvtelephone[(+358)(0)504804026]{sip:siovene@ekiga.net}
\ecvemail{\url{salvatore@iovene.com}}
%\ecvnationality{Italian}
%\ecvdateofbirth{May 9th, 1981}
%\ecvgender{Male}
%\ecvpicture[width=2cm]{mypicture}

\begin{document}
\selectlanguage{english}


\begin{europecv}
\ecvpersonalinfo[5pt]
\ecvsection{}
\ecvitem{\large\textbf{Desired employment/ Occupational field}}{\large\textbf{GNU/Linux Python/C/C++/JavaScript}}

\ecvsection{Work experience}
\ecvitem{Dates}{May 2011 - Present time}
\ecvitem{Occupation or position held}{Linux Software Engineer.}
\ecvitem{Main activities and responsibilities}{Working on middleware and UI component of the Tizen platform.}
\ecvitem{Name and address of employer}{Intel, Westendinkatu 7, 02160 ESPOO, Finland}
\ecvitem{Type of business or sector}{IT}

\ecvsection{}
\ecvitem{Dates}{January 2010 - May 20011}
\ecvitem{Occupation or position held}{Software Engineer.}
\ecvitem{Main activities and responsibilities}{Working on the core applications of Maemo 6 / MeeGo, in the realm of Instant Messaging.}
\ecvitem{Name and address of employer}{Nokia, Keilalahdentie 2-4, P.O. Box 226, FIN-00045 Nokia Group, Finland}
\ecvitem{Type of business or sector}{IT}

\ecvsection{}
\ecvitem{Dates}{March 2008 - December 2009}
\ecvitem{Occupation or position held}{Software Engineer.}
\ecvitem{Main activities and responsibilities}{Contributing to the Maemo 5 operating system. Designed and started the development of the Event Logger for Maemo 5, which has since gone Open Source: http://maemo.gitorious.org/maemo-rtcom/. Also contributed to various components in the Chat and VoIP domain.}
\ecvitem{Name and address of employer}{Digia Oyj, Hiomotie 19, Helsinki, 00380 Finland}
\ecvitem{Type of business or sector}{IT}

\ecvsection{}
\ecvitem{Dates}{September 2006 - March 2008}
\ecvitem{Occupation or position held}{Developer.}
\ecvitem{Main activities and responsibilities}{Dealing with C/C++ components spreading from low-level protocol implementation (SIP) to high level application API.}
\ecvitem{Name and address of employer}{Movial Applications, Porkkalankatu 13 J, FI-00180 Helsinki, Finland}
\ecvitem{Type of business or sector}{IT}

\ecvsection{}
\ecvitem{Dates}{December 2005 - August 2006}
\ecvitem{Occupation or position held}{Developer.}
\ecvitem{Main activities and responsibilities}{Bug fixing Maemo OS2006.}
\ecvitem{Name and address of employer}{Movial Services, Porkkalankatu 13 J, FI-00180 Helsinki, Finland}
\ecvitem{Type of business or sector}{IT}

\ecvsection{}
\ecvitem{Dates}{September 2005 - February 2006}
\ecvitem{Occupation or position held}{Developer.}
\ecvitem{Main activities and responsibilities}{J2EE development: maintainance and bug fixing for SAB Server, a centrally managed all-in-one solution that streamlines rollout of hotspot services and minimises associated costs for any service provider, operator or venue owner.}
\ecvitem{Name and address of employer}{Wificom Technologies Oy, Uudenmaankatu 11 B, FIN-00120 Helsinki, Finland}
\ecvitem{Type of business or sector}{IT}

\ecvsection{}
\ecvitem{Dates}{October 2004 - July 2005}
\ecvitem{Occupation or position held}{Developer.}
\ecvitem{Main activities and responsibilities}{Integration between Java applications and IBM Domino environment; LotusScript development aimed to workflows and Web deployment.}
\ecvitem{Name and address of employer}{Human Software SRL, Corso Garibaldi 192, 84081 Baronissi (SA), Italy}
\ecvitem{Type of business or sector}{IT}

\ecvsection{Education and training}

\ecvitem{Dates}{March 2005}
\ecvitem{Title of qualification awarded}{B.Sc. CompSci.}
\ecvitem{Principal subjects/Occupational skills covered}{Network Programming}
\ecvitem{Name and type of organization providing education and training}{Universit\'a degli Studi di Salerno}
\ecvitem{Level in national or international classification\footnote{If appropriate.}}{103/110}

\ecvsection{}
\ecvitem{Dates}{1999}
\ecvitem{Title of qualification awarded}{Scientific Liceo Diploma}
\ecvitem{Name and type of organization providing education and training}{Liceo Scientifico di Scafati}
\ecvitem{Level in national or international classification\footnote{If appropriate.}}{96/100}

\ecvsection{Personal skills and~competences}

\ecvmothertongue[5pt]{Italian}
\ecvitem{\large Other language(s)}{English, Finnish}
\ecvlanguageheader{(*)}
\ecvlanguage{English}{C1}{C1}{C1}{C1}{C1}
\ecvlanguage{Finnish}{B1}{B1}{B1}{B1}{B1}
\ecvlanguagefooter[10pt]{(*)}

\ecvitem[10pt]{\large Main technical skills and competences}{C, C++, Python, JavaScript, CoffeeScript, CSS, Less / vim, git / glib/gtk, Qt, Django}

\ecvsection{Additional information}
\ecvitem[10pt]{Personal projects}{AstroBin (http://astrobin.com/): the largest image hosting website for astrophotographers; Geek Hero Comic (http://www.geekherocomic.com/): a geeky webcomic about a hacker. }
\ecvitem{Personal interests}{Astronomy and astrophotography, jogging and cycling, reading, chess.}

\ecvsection{Get an updated copy of this CV}
\ecvitem[10pt]{PDF download}{http://www.iovene.com/cv/cv\_iovene.pdf}
\ecvitem{darcs checkout}{ darcs get http://www.iovene.com/cv}

\end{europecv}

\end{document} 
